introduction goes here.
Great stuff.~\cite{ATL-PHYS-PUB-2019-029}

Researchers in High Energy Physics (HEP) and other fields are encouraged by their funding bodies to take advantage of the High Performance Computing (HPC) facilities constructed at various institutions.
These facilities include capable machines such as Theta at Argonne National Laboratory with 280,000 cores and 192 hardware-accelerated GPUs.
While powerful, these architectures do not easily support the Python compute model.
Users must construct batch jobs and submit them to a queue for execution when compute time is available.
The results are stored on the file system and must be stitched back together once all of the jobs have completed.
On many of these systems, Python tooling lags the current state of the art and configuring modern Python libraries to use HPCs can be a tedious task and require expertise.\\

In HEP a core component of analysis of data collected at the Large Hadron Collider (LHC) is performing statistical inference for binned models to extract physics information.
The statistical fitting tools used in HEP have traditionally been implemented in C++, but in recent years pyhf, a pure-Python library with automatic differentiation and hardware acceleration, has grown in use for analysis related statistical inference problems.
The fitting of multiple different hypotheses for new physics signatures (signals) is a computational problem that lends itself easily to parallelization, but is hampered on HPC environments by the additional tooling overhead required, which can be very difficult to master.
Through use of funcX, a pure-Python high performance function serving system designed to orchestrate scientific workloads across heterogeneous computing resources, pyhf can be used as a highly scalable (fitting) function as a service (FaaS) on HPCs.\\

Through adoption of open source "tensor" computational Python libraries, pyhf is able to leverage tensor calculations to outperform the traditional C++ implementations on data from real LHC analyses.
funcX is able to create and register a service endpoint on HPC systems that interfaces with native schedulers.
End users are able to register functions through a Python API and then scalebly execute workloads, with demonstrated use of scaling to more than 100,000 workers.
We have demonstrated use of funcX to orchestrate pyhf to simultaneously fit 125 signal hypotheses in the parameter space of a published LHC physics analysis with a wall time of under 3 minutes.
The combination of pyhf and funcX reduces a common problem in HEP analyses that would traditionally take multiple hours and bespoke scheduling to an on-demand (fitting) FaaS, offering reduced time to insight and inference.\\

Through the combined use of the pure-Python libraries funcX and pyhf, we have demonstrated the ability to parallelize and accelerate statistical inference of physics analyses on HPC systems through a FaaS solution.
